%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/Miguel-Caringal/}{\Large Miguel Caringal}} & Email : \href{mailto:Miguel.Caringal@gmail.com}{Miguel.Caringal@gmail.com}\\
  \href{https://github.com/Miguel-Caringal/}{https://github.com/Miguel-Caringal/} & Mobile : 519-721-2587 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cameron Heights Collegiate Institute}{Kitchener, ON}
      {Honor Roll in all years; Subject Proficiency in Grade 12 Accounting}{Sept. 2014 -- June 2019}
    \resumeSubheading
      {St. David Catholic Secondary School}{Waterloo, ON}
      {Honor Roll Student}{Sept. 2013 -- June. 2014}
  \resumeSubHeadingListEnd


%-----------Work EXPERIENCE-----------------
\section{ Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Xylotek Solutions Inc.}{Waterloo, ON}
      {Systems Engineering Intern}{July 2018 - December 2018}
      \resumeItemListStart
        \resumeItem{}
          {Worked in an agile environment with daily standup meetings in the infrastructure/SRE team of the company's largest client, an international corporation focused on products such as POS, ITM/ATM as well as self serve checkout.}
        \resumeItem{Security: }
          {Developed an automated solution using python/powershell(PowerCLI) to ensure that development teams were Patched from both malware/ransomware such as Wannacry caused by Spectre/Meltdown Vulnerabilities, as well as ensuring that necessary security software was installed. Solution automatically sent alerts to inform teams of vulnerabilities}
        \resumeItem{VMware: }
          {Used data from VMware vCenter to generate an automated excel report created using Python (pandas). Automated script created gave the team an easy way to look at all the important vCenter information for all VMs being maintained by the team. }
        \resumeItem{Data Analysis: }
          {Used data from VMware vRealize Operations to draw conclusions of the impact of the installation/use of certain programs on the performance of Virtual Machines.}
      \resumeItemListEnd

    \resumeSubheading
      {Kumon North America}{Waterloo, ON}
      {Math and Reading Tutor}{Jan 2014 - Oct 2016}
      \resumeItemListStart
        \resumeItem{}
          {Taught Math and Reading to students from K-12, marking workbooks and answering questions. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------Volunteer EXPERIENCE-----------------
\section{Volunteer Experience}
  \resumeSubHeadingListStart

     \resumeSubheading
      {Frontier College}{Kitchener, ON}
      {Volunteer Tutor}{October 2018 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Taught all subjects to students from grades 9-12 one on one.}
      \resumeItemListEnd
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Camp Counselor}{July 2016 - August 2016}
      \resumeItemListStart
        \resumeItem{}
          {Lead science/engineering related activities for campers, ensuring that they were engaged.}
        \resumeItem{}
          {Explained/Taught science concepts to campers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CHCI Student Buddy: }
      {iOS app created to help students get around Cameron Heights (my high school), including information personalized for each student such as Student ID/Timetable. Was then selected to pitch app at D2L (Desire2Learn) and at an Apple youth developer conference to developers from both companies. In both meetings, things such as UI/Scaleability were discussed.}
    \resumeSubItem{GeoHam (First Place Hackathon Winner): }
      {Android app (Java) that takes open source datasets from the city of Hamilton and Google Cloud Platform's maps API to display local attractions to users with high amounts of detail and a clean UI. This project was made in less than 48 hours and won first place at UrbanHacks 2018. }
    \resumeSubItem{Matrix Inverse Finder: }
      {Project made in C++ that finds the inverse of an NxN matrix using Gauss-Jordan elimination, accounting for ill-conditioned matrices. }
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, C++, Swift}
    }
   \item {
        \textbf{Libraries/Frameworks}{: Pandas}
  }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
